Primal-dual algorithm for computing Nash equilibria in sequential games with imcomplete information

### 2015-01-11 nips2015.tex
ENH: getting ready for arxiv

\begin{abstract}
We present a simple primal-dual algorithm with a low cost per iteration, for computing Nash $\epsilon$-equilibria for two-person zero-sum sequential games like Texas Hold'em Poker, in $\mathcal{O}(1/\epsilon)$ iterations. %% Our algorithm is applicable to a broad class of two-person zero-sum games including simultaneous games and sequential games with imcomplete information and perfect recall. The applicability to the latter kind of games is thanks to the sequence-form representation von Stengel's \cite{von1996efficient}
Our algorithm derives from the general primal-dual algorithm developed
% by Chambolle and Pock
in \cite{chambolle2010}, which has received considerable interest in the signal processing community, but is not directly applicable to the saddle-point problem corresponding to Nash equilibria since the strategy profiles (polytopes) of players are so complex that it is not possible
% (for example, simplexes for simultaneous games, and intersections of hyperplanes and nonnegative orthants, for sequential games)
 to analytically compute
% (i.e using non-iterative procedures, etc.)
euclidean
% (metric)%
 projections (the proximal operators) thereupon.
Our technique is to dualize the linear constraints that form part of the player's strategy profile, thus obtainining an equivalent saddle-point problem which is more amendable to the primal-dual scheme, without any additional overhead. The resulting algorithm is simple, only involving matrix-vector multiplications
% (without any matrix inversions, etc.)
and nonnegative clipping.
% (taking point-wise max of a vector and 0)
The $\mathcal{O}(1/\epsilon)$ convergence rate of our algorithm derives explicitly from the general primal-dual algorithm in \cite{chambolle2010}. Unlike the EGT (Excessive Gap Technique) recently used in \cite{hoda2010smoothing}, our algorithm has a cheap and constant cost per iteration. As proof of concept, we apply our algorithm to solve Kuhn Poker.
%% We conclude by extending our results to tackle Nash equilibrium problems with even more general strategy profiles, where the nonnegativity constraints on realization plans are replaced with more general convex sets.
\end{abstract}

\section{Introduction}
\label{sec:intro}
For sequential games with imcomplete information and perfect recall like Texas Hold'em Poker, von Stengel and co-workers have developed the \textit{sequence-form} representation (see \cite{von1996efficient} and references therewithin), whose size is linear in the size of the game tree, in contrast with the \textit{strategic-form} representation which is exponential. The goal of this paper is to develop a fast and simple primal-dual algorithm for computing Nash equilibria for such games, using this representation.

In \cite{von1996efficient, vonequilibrium}, it was established that for sequential two-person zero-sum games with imcomplete information and perfect recall, there exist sparse matrices $A \in \mathbb{R}^{n_1 \times n_2}, E_1 \in \mathbb{R}^{l_1 \times n_1}, E_2 \in \mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in \mathbb{R}^{l_1}, e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$, $l_1$, and $l_2$ are all linear in the size of the game tree (number of states in the game) and such that Nash equilibria correspond to pairs $(x, y)$ of \textit{realization plans} which solve the primal LCP (Linear Constrained Programming) problem
\begin{equation}
  \begin{aligned}
    & \underset{y,p}{\text{minimize}}
    & & e_1^Tp \\
    & \text{subject to}
    & & -Ay + E_1^Tp \geq 0,\\
    &&& E_2y = e_2,\\
    &&& y \ge 0
  \end{aligned}
  \label{eq:primal_pb}
\end{equation}

@@

with \textit{duality gap} given by
\begin{equation}
  \mathcal{G}(p, q) := e_1^Tp - (-e_2^Tq) = e_1^Tp + e_2^Tq
  \label{eq:dgap}
\end{equation}

$A$ is the \textit{payoff matrix} and each $E_k$ is a matrix whose entries are $-1$, $0$ or $1$, and $e_k$ is a vector of the form $[1, 0, ..., 0]$. In this representation (called the \textit{sequence-form}), the strategy profile of player $k$ is the polytope
\begin{equation}
  Q_k := \{z \ge 0\text{ }|\text{ }E_kz = e_k\} \subseteq \mathbb{R}^{n_k}
\end{equation}

Of course by \textit{weak duality} in problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb}, it holds that
\begin{equation}
  \mathcal{G}(p, q) \geq 0
\end{equation}
for any fixed pair $(x, y)$ of realization plans and admissible dual pair $(p,q)$ in problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb}.

@@

%% We can distinguish two categories of such games, in terms of (non-)simultaneity of play.
%% \paragraph{Simultaneous two-person zero-sum games}
%% \label{subsec:example_games}
%% Here, the Nash equilibrium problem takes the form \eqref{eq:primal_pb} with $l_k = 1$, $C_k = \mathbb{R}^{l_k}_+$, $E_k = 1_{1, n_k}$,
%%   and $e_k = 1$, so that $Q_k$ is simply the probabability $n_k$-simplex $\Delta_{n_k}$. Each point in $\Delta_{n_k}$ corresponds to a \textit{mixed-strategy} for player $j$,
%% and represents a randomization on their \textit{pure-strategies} (corresponding to the vertices of their propability simplex $\Delta_{n_k}$).

%% \paragraph{Two-person zero-sum sequential games with imcomplete information and perfect recall}
%% It is now known, thanks to the \textit{sequence-form representaion}, that the Nash equilibrium problem for such games takes the form \eqref{eq:primal_pb}.

@@

%% \paragraph{Example of Nash equilibirum}
%% As an illustration, the pair $(x^*, y^*)$ given by
%% $x^* = [1, .478, .522, .174, .826]^T$ and
%% $y^* = [1, 1/2, 1/2]^T$ is a Nash equilibrium for the sequence-form game given by (not showing zero entries)\\
%% $A = \left[\begin{array}{ccc}
%%   &   &  \\
%%   &   &  \\
%%   & 1 & -1\\
%%   & -2 & 4\\
%% 1 &   &  
%% \end{array}\right]$, $E_1 = \left[\begin{array}{ccccc}
%%   1 &   &   &   &  \\
%%   -1 & 1 & 1 &   &  \\
%%   -1 &   &   & 1 & 1
%% \end{array}\right]$,
%% $E_2 = \left[\begin{array}{ccc}
%%   1 &   &  \\
%%   -1 & 1 & 1
%% \end{array}\right]$, $e_1 = [1, 0, 0]^T$, and $e_2 = [1, 0]^T$.

Solving problem \eqref{eq:primal_pb} exactly is impossible in practice, and such a precision doesn't have any fundamental advantage. Instead, it is customary compute so-called Nash $\epsilon$-equlibria

@@

\paragraph{Outline of article}
The goal of this article is to device a simple algorithm which produces a Nash $\epsilon$-equilibrium after $\mathcal{O}(1/\epsilon)$ iterations%We first briefly introduce the sequence-form representation, and contrast it to the strategic-form representation. Then we state the Nash equilibrium problem for the sequence-form representation. Then in
In section \ref{sec:related_work}, we give a brief overview of existing methods for solving \eqref{eq:approx_pb}. In section \ref{sec:algo} we derive the proposed algorithm for solving this problem and prove its $\mathcal{O}(1/\epsilon)$ convergence rate. With construct with a demonstration on Kuhn 3-card Poker.

@@

%%%
%% \section{The sequence-form representation}
%% \label{sec:rep}
%% \paragraph{Recap: Extensive-form representation} The game tree $\mathcal{T}$ is defined as follows. There are three players: player 1 (Alice), player 2 (Bob), and player 0, a special player called \textit{chance}. All three players are treated symmetrically. Nodes of the game tree $\mathcal{T}$ are identified with states of the game, and actions taken by players correspond to edges of $\mathcal{T}$.
%% The players take turns to play according to the rules of the game, until a terminal node (aka \textit{leaf}) is reached upon which the game automatically stops. %% The sequence-form is similar to the \textit{extensive-form} except that in the latter, pure strategies are defined on edges, whilst they're defined on paths (sequences of ordered choices) in the former.
%% At each node $t$ of $\mathcal{T}$, a unique player \textit{acts} (ie take their turn), referred to as the \textit{player to act} at the given node. This way, the nodes of the game tree are partitioned into three classes: the nodes at which the chance player acts (e.g the root node), the nodes at which Alice acts, and the nodes at which Bob acts. Due to imcompleted information, each player's nodes are grouped into equivalent classes of \textit{strategically indistinguishable} nodes called \textit{information sets}; $\mathcal{I}_k$ is the set of all information sets of player $k$. If each information set is a singleton, then the game reduces to a game complete information.

%% $a(t)$ is the \textit{payoff} received by player $1$ at node $t$. That the game is zero-sum means that player 2
%% receives a payoff of $-a(t)$. Note that $a(t)$ is $0$ for all non-leaf nodes, since the game must continue.
%% The goal of a \textit{rational} player is that the game should end at a node for which her payoff is as large as possible.
%% We will assume implicitly that each (non-chance) player is rational.

%% A \textit{mixed-strategy} for a player is specified by a prescription of the probability of making a given choice from a given node at which the player acts. The chance player plays a publicly known \textit{mixed strategy} $\beta_0$.

%% \paragraph{From extensive-form to sequence-form representation}
%% For each information set $h$ of player $k$, $\sigma_h$ (unique and well-defined, by the  is the sequence of choices from the root node, to --any node of-- $h$, ignoring the choices of the other players. \textit{perfect recall} means that a player cannot get additional information on the game tree by remembering their earlier choices, and so $\sigma_h$ is well-defined. $C_h$ is the set of choices at $h$. The set of \textit{sequences} of player $k$, denoted $\mathcal{S}_k$, is defined by 
%% \begin{equation}
%% \mathcal{S}_k := \{\emptyset\} \cup \{\sigma_h c\text{ } |\text{ } h \in I_k, c \in C_h\}
%% \end{equation}
%% Each element $\sigma$ of $\mathcal{S}_k$ is a path joining the root node to a leaf in the game tree, with the choices of all other players deleted, and represents a possible sequence of choices made by player $k$ in the game, from start to finish. $\sigma_k(t)$ is the unique sequence in $\mathcal{S}_k$ which can be extended to the path from root to node $t$, by including the choices of the other players;
%% $\beta_0(t)$ is the product of the probabilities of the choices made by the chance player along $\sigma_0(t)$.

%% Player $k$'s \textit{pure-strategies} correspond to points in $\prod_{h \in \mathcal{I}_k}{\mathcal{C}_h}$, and their \textit{mixed-strategies} are randomizations on these pure-strategies. In sequence-form, the strategy profile $Q_k$ of player $k \ge 1$ is the polytope of $n_k$-dimensional nonnegative vectors satisying
%% % Besides nonnegativity, the \textit{realization plans} $z$ of each play $k>0$ must obey linear contraints of the form
%% \begin{equation}
%%     z(\emptyset) = 1 \text{ and }
%%     z(\sigma_h) - \sum_{c \in C_h}{z(\sigma_h c)} = 0\text{, } \forall h \in \mathcal{I}_k
%%   \label{eq:lin}
%% \end{equation}

%% These linear constraints \eqref{eq:lin} can be succinctly written as $E_k z = e_k$,
%% where $E_k$ is a matrix with $l_k := 1 + \#\mathcal{I}_k$ rows and $n_k := \#\mathcal{S}_k$ columns whose entries are either $-1$, $0$, or $1$, and $e_k$ is $l_k$-dimensional vector of the form $(1, 0, ..., 0)$. Thus we can re-write

%% \begin{equation}
%%   Q_k := \{z \in \mathbb{R}^{n_k}| z \ge 0\text{ and }E_kz = e_k\}
%%   \label{eq:poly}
%% \end{equation}

%% Each point $z \in Q_k$ is called a \textit{realization plan} and induces a \textit{behavioural-strategy} $\beta_k$ such that for each information set $h \in \mathcal{I}_k$ and each choice $c \in C_h$, the probability for player $k$ to make a choice $c \in \mathcal{C}_h$ from any node in $h$ is
%% \begin{equation}
%%   \beta_k(h, c) := \begin{cases}
%%     z(\sigma_hc)/z(\sigma_h), é\mbox{if } z(\sigma_h) > 0\\
%%     0, &\mbox{Otherwise}.
%%   \end{cases}
%% \end{equation}

%% From this definition, it is clear that each behavioural-strategy is equivalent to a mixed-strategy.

%% The payoff matrix from player 1's perspective is the the $n_1$-by-$n_2$ matrix $A = (A_{\sigma,\tau})$ defined by
%% \begin{equation}
%%     A_{\sigma,\tau} := \sum_{\text{leafs }t\text{ : } \sigma_1(t) = \sigma\text{ and } \sigma_2(t) = \tau}{\beta_0(t)a(t)}, \forall (\sigma, \tau) \in \mathcal{S}_1 \times \mathcal{S}_2
%%   \end{equation}

%% If player 1 plays strategy $x \in Q_1$ and player 2 plays strategy $y \in Q_2$ then player 1 gets $x^TAy$ units of money; that the game is ``zero-sum'' means that player 2 gets $-x^TAy$.

%% The nanuplet $(\mathcal{I}_1, \mathcal{I}_2, \mathcal{S}_1, \mathcal{S}_2, A, E_1, E_2, e_1, e_2)$ completely specifies a game in sequence-form. However, since are only interested in computing Nash equilibria, the quintuplet $(A, E_1, E_2, e_1, e_2)$ conveys all the needed data.

%% \paragraph{Example: Sequence-form representation of Kuhn Poker}
%% \label{sec:kuhn_sf}
%% The Kuhn 3-card Poker has sequence-form specification given by (not showing zero entries)\\
%% $A = \left[\begin{array}{ccccccccccccc}
%%   &   &   &   &   &   &   &   &   &   &   &   &  \\
%%   &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6 &  \\
%%   &   &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6\\
%%   &   &   &   &   &   &   &   & -1 / 3 &   &   &   & -1 / 3\\
%%   &   &   &   &   & 1 / 6 & -1 / 3 &   &   & 1 / 6 & -1 / 3 &   &  \\
%%   &   &   & 1 / 6 &   &   &   &   &   &   &   & -1 / 6 &  \\
%%   &   &   &   & -1 / 6 &   &   &   &   &   &   &   & -1 / 6\\
%%   &   &   &   & 1 / 3 &   &   &   &   &   &   &   & -1 / 3\\
%%   & 1 / 6 & 1 / 3 &   &   &   &   &   &   & 1 / 6 & -1 / 3 &   &  \\
%%   &   &   & 1 / 6 &   &   &   & 1 / 6 &   &   &   &   &  \\
%%   &   &   &   & -1 / 6 &   &   &   & -1 / 6 &   &   &   &  \\
%%   &   &   &   & 1 / 3 &   &   &   & 1 / 3 &   &   &   &  \\
%%   & 1 / 6 & 1 / 3 &   &   & 1 / 6 & 1 / 3 &   &   &   &   &   &  
%% \end{array}\right]$,\\
%% $E_1 = \left[\begin{array}{ccccccccccccc}
%% 1 &   &   &   &   &   &   &   &   &   &   &   &  \\
%% -1 &   &   &   &   &   &   &   &   & 1 &   &   & 1\\
%% -1 & 1 &   &   & 1 &   &   &   &   &   &   &   &  \\
%% -1 &   &   &   &   & 1 &   &   & 1 &   &   &   &  \\
%%   & -1 & 1 & 1 &   &   &   &   &   &   &   &   &  \\
%%   &   &   &   &   & -1 & 1 & 1 &   &   &   &   &  \\
%%   &   &   &   &   &   &   &   &   & -1 & 1 & 1 &  
%% \end{array}\right]$, $e_1 = e_2 = [1, 0, 0, 0, 0, 0, 0]^T$,\\
%% and $E_2 = \left[\begin{array}{ccccccccccccc}
%% 1 &   &   &   &   &   &   &   &   &   &   &   &  \\
%% -1 &   &   &   &   &   &   & 1 & 1 &   &   &   &  \\
%% -1 &   &   &   &   &   &   &   &   & 1 & 1 &   &  \\
%% -1 &   &   &   &   & 1 & 1 &   &   &   &   &   &  \\
%% -1 &   &   &   &   &   &   &   &   &   &   & 1 & 1\\
%% -1 & 1 & 1 &   &   &   &   &   &   &   &   &   &  \\
%% -1 &   &   & 1 & 1 &   &   &   &   &   &   &   &  
%% \end{array}\right]$.\\

\section{Related work}
\label{sec:related_work}
In \cite{hoda2010smoothing}, a nested iterative procedure using the Excessive Gap Technique \cite{nesterov2005excessive} was used to to solve the LCP problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} in the following equivalent saddle-point form

\begin{equation}
  \underset{y \in Q_2}{\text{minimize}}\text{ }\underset{x \in Q_1}{\text{maximize}}\text{ }x^TAy
\end{equation}

@@

@@

\section{The proposed algorithm}
\label{sec:algo}
We now derive our primal-dual algorithm for solving the Nash equilibrium problem \eqref{eq:primal_pb}. The algorithm is obtained from the general primal-dual Algorithm 39 proposed in \cite{chambolle2010}. Though this scheme has recently gained considerable popularity in the signal processing community
%\cite{gramfort-etal:2013a}
, to the best of our knowledge, this is the first time it is being applied to compute Nash equilibria.

>>>>

\begin{abstract}
We present a simple primal-dual algorithm with a low cost per iteration, for computing Nash $\epsilon$-equilibria for two-person zero-sum sequential games like Texas Hold'em Poker, which converges --in duality gap-- after $\mathcal{O}(1/\epsilon)$ basic iterations (i.e iterations only involving basic operations like matvec, clipping, etc., and no calls to external oracles). %% Our algorithm is applicable to a broad class of two-person zero-sum games including simultaneous games and sequential games with imcomplete information and perfect recall. The applicability to the latter kind of games is thanks to the sequence-form representation von Stengel's \cite{von1996efficient}
Our algorithm derives from the general primal-dual algorithm developed
% by Chambolle and Pock
in \cite{chambolle2010}, which has received considerable interest in the signal processing community, but is not directly applicable to the saddle-point problem corresponding to Nash equilibria since the strategy profiles (polytopes) of players are so complex that it is not possible
% (for example, simplexes for simultaneous games, and intersections of hyperplanes and nonnegative orthants, for sequential games)
 to analytically compute
% (i.e using non-iterative procedures, etc.)
euclidean
% (metric)%
 projections (the proximal operators) thereupon.
Our technique is to dualize the linear constraints that form the player's strategy profile, thus obtainining an equivalent saddle-point problem which is more amendable to the primal-dual scheme, without any additional overhead. The resulting algorithm is simple, only involving matrix-vector multiplications
% (without any matrix inversions, etc.)
and nonnegative clipping.
% (taking point-wise max of a vector and 0)
The $\mathcal{O}(1/\epsilon)$ convergence rate of our algorithm derives explicitly from the general primal-dual algorithm in \cite{chambolle2010}. Unlike the EGT (Excessive Gap Technique) recently used in \cite{hoda2010smoothing}, our algorithm has a cheap and constant cost per iteration. As proof of concept, we apply our algorithm to solve Kuhn 3-card Poker \cite{kuhn}.
%% We conclude by extending our results to tackle Nash equilibrium problems with even more general strategy profiles, where the nonnegativity constraints on realization plans are replaced with more general convex sets.
\end{abstract}

\section{Introduction}
\label{sec:intro}
For sequential games with imcomplete information and perfect recall like Texas Hold'em Poker, von Stengel and co-workers have developed the \textit{sequence-form} representation (see \cite{von1996efficient} and references therewithin), whose size is linear in the size of the game tree, in contrast with the \textit{strategic-form} representation which is exponential. The goal of this paper is to develop a fast and simple primal-dual algorithm for computing  Nash $\epsilon$-equilibria for such games, using this representation.

\subsection{Context}
In \cite{von1996efficient, vonequilibrium}, it was established that for sequential two-person zero-sum games with imcomplete information and perfect recall, there exist sparse matrices $A \in \mathbb{R}^{n_1 \times n_2}, E_1 \in \mathbb{R}^{l_1 \times n_1}, E_2 \in \mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in \mathbb{R}^{l_1}, e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$, $l_1$, and $l_2$ are all linear in the size of the game tree (number of states in the game) and such that Nash equilibria correspond to pairs $(x, y)$ of \textit{realization plans} which solve the primal LCP (Linear Constrained Programming) problem
\begin{equation}
  \begin{aligned}
    & \underset{y,p}{\text{minimize}}
    & & e_1^Tp \\
    & \text{subject to}
    & & -Ay + E_1^Tp \geq 0,\\
    &&& E_2y = e_2,\\
    &&& y \ge 0
  \end{aligned}
  \label{eq:primal_pb}
\end{equation}

@@

with \textit{duality gap} given by\footnote{The last inequality being due to \textit{week duality}.}
\begin{equation}
  \mathcal{G}(p, q) := e_1^Tp - (-e_2^Tq) = e_1^Tp + e_2^Tq \geq 0
  \label{eq:dgap}
\end{equation}

$A$ is the \textit{payoff matrix} and each $E_k$ is a matrix whose entries are $-1$, $0$ or $1$, and $e_k$ is a vector of the form $[1, 0, ..., 0]$. In this representation (called the \textit{sequence-form}), the strategy profile of player $k$ is the polytope
\begin{equation}
  Q_k := \{z \ge 0\text{ }|\text{ }E_kz = e_k\} \subseteq \mathbb{R}^{n_k}
\label{eq:polytope}
\end{equation}

@@

%% We can distinguish two categories of such games, in terms of (non-)simultaneity of play.
%% \subsection{Simultaneous two-person zero-sum games}
%% \label{subsec:example_games}
%% Here, the Nash equilibrium problem takes the form \eqref{eq:primal_pb} with $l_k = 1$, $C_k = \mathbb{R}^{l_k}_+$, $E_k = 1_{1, n_k}$,
%%   and $e_k = 1$, so that $Q_k$ is simply the probabability $n_k$-simplex $\Delta_{n_k}$. Each point in $\Delta_{n_k}$ corresponds to a \textit{mixed-strategy} for player $j$,
%% and represents a randomization on their \textit{pure-strategies} (corresponding to the vertices of their propability simplex $\Delta_{n_k}$).

%% \subsection{Two-person zero-sum sequential games with imcomplete information and perfect recall}
%% It is now known, thanks to the \textit{sequence-form representaion}, that the Nash equilibrium problem for such games takes the form \eqref{eq:primal_pb}.

@@

%% \subsection{Example of Nash equilibirum}
%% As an illustration, the pair $(x^*, y^*)$ given by
%% $x^* = [1, .478, .522, .174, .826]^T$ and
%% $y^* = [1, 1/2, 1/2]^T$ is a Nash equilibrium for the sequence-form game given by (not showing zero entries)\\
%% $A = \left[\begin{array}{ccc}
%%   &   &  \\
%%   &   &  \\
%%   & 1 & -1\\
%%   & -2 & 4\\
%% 1 &   &  
%% \end{array}\right]$, $E_1 = \left[\begin{array}{ccccc}
%%   1 &   &   &   &  \\
%%   -1 & 1 & 1 &   &  \\
%%   -1 &   &   & 1 & 1
%% \end{array}\right]$,
%% $E_2 = \left[\begin{array}{ccc}
%%   1 &   &  \\
%%   -1 & 1 & 1
%% \end{array}\right]$, $e_1 = [1, 0, 0]^T$, and $e_2 = [1, 0]^T$.

\subsection{Statement of the problem}
Solving problem \eqref{eq:primal_pb} exactly is impossible in practice, and such a precision doesn't have any fundamental advantage. Instead, it is customary compute so-called Nash $\epsilon$-equlibria

@@

The goal of this article is to device a simple algorithm which produces a Nash $\epsilon$-equilibrium after $\mathcal{O}(1/\epsilon)$ iterations%We first briefly introduce the sequence-form representation, and contrast it to the strategic-form representation. Then we state the Nash equilibrium problem for the sequence-form representation. Then in

\subsection{Outline of the article}
In section \ref{sec:rep} we briefly review the sequence-form representation. In section \ref{sec:related_work}, we give a brief overview of existing methods for computing Nash $\epsilon$-equilibria. Section \ref{sec:notation} features useful notions of convex optimization (proximal operators, convex conjugates, etc.). In section \ref{sec:algo} we derive the proposed algorithm for solving this problem and prove its $\mathcal{O}(1/\epsilon)$ convergence rate. We conclude with a demonstration on Kuhn 3-card Poker \cite{kuhn}.

@@

\section{The sequence-form representation}
\label{sec:rep}
In this section, we briefly recall the sequence-form representation of sequential games with imcomplete information and perfect recall. A complete overview of the subject can be found in the pioneering work \cite{von1996efficient}.
\subsection{Recap: Extensive-form representation} The game tree $\mathcal{T}$ is defined as follows. There are three players: player 1 (Alice), player 2 (Bob), and player 0, a special player called \textit{chance}. All three players are treated symmetrically. Nodes of the game tree $\mathcal{T}$ are identified with states of the game, and actions taken by players correspond to edges of $\mathcal{T}$.
The players take turns to play according to the rules of the game, until a terminal node (aka \textit{leaf}) is reached upon which the game automatically stops. %% The sequence-form is similar to the \textit{extensive-form} except that in the latter, pure strategies are defined on edges, whilst they're defined on paths (sequences of ordered choices) in the former.
At each node $t$ of $\mathcal{T}$, a unique player \textit{acts} (ie take their turn), referred to as the \textit{player to act} at the given node. This way, the nodes of the game tree are partitioned into three classes: the nodes at which the chance player acts (e.g the root node), the nodes at which Alice acts, and the nodes at which Bob acts. Due to imcompleted information, each player's nodes are grouped into equivalent classes of \textit{strategically indistinguishable} nodes called \textit{information sets}; $\mathcal{I}_k$ is the set of all information sets of player $k$. If each information set is a singleton, then the game reduces to a game complete information.

$a(t)$ is the \textit{payoff} received by player $1$ at node $t$. That the game is zero-sum means that player 2
receives a payoff of $-a(t)$. Note that $a(t)$ is $0$ for all non-leaf nodes, since the game must continue.
The goal of a \textit{rational} player is that the game should end at a node for which her payoff is as large as possible.
We will assume implicitly that each (non-chance) player is rational.

A \textit{mixed-strategy} for a player is specified by a prescription of the probability of making a given choice from a given node at which the player acts. The chance player plays a publicly known \textit{mixed strategy} $\beta_0$.

\subsection{From extensive-form to sequence-form representation}
For each information set $h$ of player $k$, $\sigma_h$ (unique and well-defined, by the  is the sequence of choices from the root node, to --any node of-- $h$, ignoring the choices of the other players. \textit{perfect recall} means that a player cannot get additional information on the game tree by remembering their earlier choices, and so $\sigma_h$ is well-defined. $C_h$ is the set of choices at $h$. The set of \textit{sequences} of player $k$, denoted $\mathcal{S}_k$, is defined by 
\begin{equation}
\mathcal{S}_k := \{\emptyset\} \cup \{\sigma_h c\text{ } |\text{ } h \in I_k, c \in C_h\}
\end{equation}
Each element $\sigma$ of $\mathcal{S}_k$ is a path joining the root node to a leaf in the game tree, with the choices of all other players deleted, and represents a possible sequence of choices made by player $k$ in the game, from start to finish. $\sigma_k(t)$ is the unique sequence in $\mathcal{S}_k$ which can be extended to the path from root to node $t$, by including the choices of the other players;
$\beta_0(t)$ is the product of the probabilities of the choices made by the chance player along $\sigma_0(t)$.

Player $k$'s \textit{pure-strategies} correspond to points in $\prod_{h \in \mathcal{I}_k}{\mathcal{C}_h}$, and their \textit{mixed-strategies} are randomizations on these pure-strategies. In sequence-form, the strategy profile of player $k \ge 1$ is the polytope of $n_k$-dimensional nonnegative vectors $z$ (a realization plan) satisfying
% Besides nonnegativity, the \textit{realization plans} $z$ of each play $k>0$ must obey linear contraints of the form
\begin{equation}
  z \geq 0,\hspace{1em}z(\emptyset) = 1,\hspace{1em}
    z(\sigma_h) - \sum_{c \in C_h}{z(\sigma_h c)} = 0\text{, } \forall h \in \mathcal{I}_k
  \label{eq:lin}
\end{equation}

These linear constraints \eqref{eq:lin} can be succinctly written as $E_k z = e_k$,
where $E_k$ is a matrix with $l_k := 1 + \#\mathcal{I}_k$ rows and $n_k := \#\mathcal{S}_k$ columns whose entries are either $-1$, $0$, or $1$, and $e_k$ is $l_k$-dimensional vector of the form $(1, 0, ..., 0)$. The polytopes $Q_k$ defined already in \eqref{eq:polytope} coincide with the constraints \eqref{eq:lin}. Given a player $k$, each realization plan $z \in Q_k$ induces a \textit{behavioural-strategy} $\beta_k$ such that for each information set $h \in \mathcal{I}_k$ and each choice $c \in C_h$, the probability for player $k$ to make choice $c$ from any node in $h$ is
\begin{equation}
  \beta_k(h, c) := \begin{cases}
    z(\sigma_hc)/z(\sigma_h), é\mbox{if } z(\sigma_h) > 0\\
    0, &\mbox{Otherwise}.
  \end{cases}
\end{equation}

From this definition, it is clear that each behavioural-strategy is equivalent to a mixed-strategy.

The payoff matrix from player 1's perspective is the the $n_1$-by-$n_2$ matrix $A = (A_{\sigma,\tau})$ defined by
\begin{equation}
    A_{\sigma,\tau} := \sum_{\text{leafs }t\text{ : } \sigma_1(t) = \sigma\text{ and } \sigma_2(t) = \tau}{\beta_0(t)a(t)}, \forall (\sigma, \tau) \in \mathcal{S}_1 \times \mathcal{S}_2
  \end{equation}

If player 1 plays strategy $x \in Q_1$ and player 2 plays strategy $y \in Q_2$ then player 1 gets $x^TAy$ units of money; that the game is ``zero-sum'' means that player 2 gets $-x^TAy$.

The nanuplet $(\mathcal{I}_1, \mathcal{I}_2, \mathcal{S}_1, \mathcal{S}_2, A, E_1, E_2, e_1, e_2)$ completely specifies a game in sequence-form and the LCP problems correspond to the Nash \textit{minimax} problem for such games. However, since are only interested in computing Nash equilibria, the quintuplet $(A, E_1, E_2, e_1, e_2)$ conveys all the needed data.

\subsection{Example: Sequence-form representation of Kuhn Poker}
\label{sec:kuhn_sf}
The Kuhn 3-card Poker \cite{kuhn} has sequence-form specification given by (not showing zero entries)\\
$A = \left[\begin{array}{ccccccccccccc}
  &   &   &   &   &   &   &   &   &   &   &   &  \\
  &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6 &  \\
  &   &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6\\
  &   &   &   &   &   &   &   & -1 / 3 &   &   &   & -1 / 3\\
  &   &   &   &   & 1 / 6 & -1 / 3 &   &   & 1 / 6 & -1 / 3 &   &  \\
  &   &   & 1 / 6 &   &   &   &   &   &   &   & -1 / 6 &  \\
  &   &   &   & -1 / 6 &   &   &   &   &   &   &   & -1 / 6\\
  &   &   &   & 1 / 3 &   &   &   &   &   &   &   & -1 / 3\\
  & 1 / 6 & 1 / 3 &   &   &   &   &   &   & 1 / 6 & -1 / 3 &   &  \\
  &   &   & 1 / 6 &   &   &   & 1 / 6 &   &   &   &   &  \\
  &   &   &   & -1 / 6 &   &   &   & -1 / 6 &   &   &   &  \\
  &   &   &   & 1 / 3 &   &   &   & 1 / 3 &   &   &   &  \\
  & 1 / 6 & 1 / 3 &   &   & 1 / 6 & 1 / 3 &   &   &   &   &   &  
\end{array}\right]$,\\
$E_1 = \left[\begin{array}{ccccccccccccc}
1 &   &   &   &   &   &   &   &   &   &   &   &  \\
-1 &   &   &   &   &   &   &   &   & 1 &   &   & 1\\
-1 & 1 &   &   & 1 &   &   &   &   &   &   &   &  \\
-1 &   &   &   &   & 1 &   &   & 1 &   &   &   &  \\
  & -1 & 1 & 1 &   &   &   &   &   &   &   &   &  \\
  &   &   &   &   & -1 & 1 & 1 &   &   &   &   &  \\
  &   &   &   &   &   &   &   &   & -1 & 1 & 1 &  
\end{array}\right]$, $e_1 = e_2 = [1, 0, 0, 0, 0, 0, 0]^T$,\\
and $E_2 = \left[\begin{array}{ccccccccccccc}
1 &   &   &   &   &   &   &   &   &   &   &   &  \\
-1 &   &   &   &   &   &   & 1 & 1 &   &   &   &  \\
-1 &   &   &   &   &   &   &   &   & 1 & 1 &   &  \\
-1 &   &   &   &   & 1 & 1 &   &   &   &   &   &  \\
-1 &   &   &   &   &   &   &   &   &   &   & 1 & 1\\
-1 & 1 & 1 &   &   &   &   &   &   &   &   &   &  \\
-1 &   &   & 1 & 1 &   &   &   &   &   &   &   &  
\end{array}\right]$.\\

\section{Related work}
\label{sec:related_work}
\paragraph{Smoothing methods}
In \cite{hoda2010smoothing}, a nested iterative procedure using the Excessive Gap Technique \cite{nesterov2005excessive} was used to to solve the LCP problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} in the following equivalent saddle-point form

\begin{equation}
  \underset{y \in Q_2}{\text{minimize}}\text{ }\underset{x \in Q_1}{\text{maximize}}\text{ }x^TAy
  \label{eq:gilpin}
\end{equation}

@@

In \cite{gilpinfirst}, a modified verson of the technqiues of \cite{hoda2010smoothing} was developed. The authors proved a $\mathcal{O}\left(\left(\|A\| / \delta\right) ln\left(1 / \epsilon\right)\right)$ convergence rate in terms of the number of calls made to a first-order oracle (for example, Nesterov's optimal gradient \cite{nesterov1983}). Here $\delta = \delta(A, E_1, E_2, e_1, e_2)$ is a \textit{condition number} for the given game.
It should be noted however that
\begin{itemize}
\item Though the authors in \cite{gilpinfirst} proved that $\delta > 0$ always, this constant can be arbitrarily small.\item The reported linear convergence rate is not in terms of basic operations (addition, multiplication, matvec, clipping, etc.), but in terms of number of calls to a first-order oracle. %% Thus the algorithm developed in \cite{gilpinfirst} doesn't have linear convergence rate in terms of fundamental operations (addition, multiplication, matvec, clipping, etc.).
  \item Of course, the existence of a linear algorithm for solving \eqref{eq:gilpin} is improbable, as the usual strong-convexity conditions are absent.
\end{itemize}

\paragraph{CounterFactual Regret minimization}
More recently, the primal-dual algorithm was applied to matrix games (on simplexes) in \cite{chambolle2014ergodic}. Sampling techniques like the CFR (CounterFactual Regret minimization) and its many variants \cite{MartinZinkevichNIPS2007, lanctot2009monte} are also becoming popular...

@@

\section{The proposed algorithm}
\label{sec:algo}
We now present our main contribution, namely an $\mathcal{O}(1/\epsilon)$ primal-dual algorithm for computing Nash $\epsilon$-equilibria for sequential two-person zero-sum games with imcomplete information and perfect recall. The algorithm is obtained from the general primal-dual Algorithm 39 proposed in \cite{chambolle2010}.
